\section{Tài liệu tham khảo}
\begin{thebibliography}{1}
		
	\bibitem{observer}
	Design Pattern - Observer. Truy cập tại \url{https://viblo.asia/p/design-pattern-observer-V3m5WO8W5O7}
	
	\bibitem{observer2}
	Observer Design Pattern - Trợ thủ đắc lực của Developers.Truy cập tại
	\url{https://viblo.asia/p/observer-design-pattern-tro-thu-dac-luc-cua-developers-gAm5y7WAZdb}

	
	\bibitem{DI} Dependency Injection Design Pattern in C\#. Truy cập tại \url{https://dotnettutorials.net/lesson/dependency-injection-design-pattern-csharp/}
	
	\bibitem{SQL}
	SQL (Ngôn ngữ truy vấn có cấu trúc) là gì? Truy cập tại \url{https://aws.amazon.com/vi/what-is/sql/}
	
	\bibitem{CSharp}
	Microsoft Corporation. \textit{C\# Language Specification}. Truy cập tại \url{https://learn.microsoft.com/en-us/dotnet/csharp/language-reference/language-specification/introduction}.
	
	\bibitem{unity}
	Unity Technologies. \textit{Unity Game Engine}. Truy cập tại \url{https://unity.com}.
	
	
	\bibitem{leveldesign1} Game Level Design: How to Do It and With What Tools. Truy cập tại \url{https://starloopstudios.com/game-level-design-how-to-do-it-and-with-what-tools/}
	
	\bibitem{leveldesign2} Video Game Level Design. Truy cập tại \url{https://www.nuclino.com/articles/level-design}
	
	\bibitem{leveldesign3} Game Level Design Beyond Design: Learn from these Tutorials, Techniques, and Do’s \& Don’ts. Truy cập tại \url{https://www.gamedesigning.org/learn/level-creation-tutorials/#Level-Designs-Game-Environments}
	
	\bibitem{sqlmurdermystery} Game Level Design Beyond Design: Learn from these Tutorials, Techniques, and Do’s \& Don’ts. Truy cập tại \url{https://www.gamedesigning.org/learn/level-creation-tutorials/#Level-Designs-Game-Environments}
	
	\bibitem{mini_airways_store}
	Valve Corporation. \textit{Mini Airways on Steam}. Available from: \url{https://store.steampowered.com/app/2289650/Mini_Airways/}.
	
	\bibitem{mini_airways_kickstarter}
	NPA Games. \textit{Mini Airways Kickstarter Campaign: Direct the Flight, Rise to the Challenge}. Available from: \url{https://www.kickstarter.com/projects/npa/direct-the-flight-rise-to-the-challenge-in-mini-airways}.
	
	\bibitem{mini_railway_steamdb}
	Valve Corporation. \textit{Mini Railway on Steam Community}. Available from: \url{https://steamcommunity.com/app/1275650/?curator_clanid=4777282&utm_source=SteamDB}.
	
	\bibitem{mini_railway_game_stats}
	Game Stats. \textit{Mini Railway - Steam Game Stats}. Available from: \url{https://games-stats.com/steam/game/mini-railway/}.
	
	\bibitem{simple_trains_steam_community}
	Valve Corporation. \textit{Simple Trains on Steam Community}. Available from: \url{https://steamcommunity.com/app/2095480}.
	
	\bibitem{simple_trains_store}
	Valve Corporation. \textit{Simple Trains on Steam}. Available from: \url{https://store.steampowered.com/app/2095480/Simple_Trains/}.
	
	
	\bibitem{stern2019overview}
	Stern, R. (2019). Multi-Agent Path Finding – An Overview. In: \textit{Lecture Notes in Computer Science}, 10.1007/978-3-030-33274-7\_6.
	
	\bibitem{stern2019}
	Stern, R., Sturtevant, N.R., Felner, A., Keonig, S., Ma, H., Walker, T.T., Li, J., Atzmon, D., Cohen, L., Kumar, T.S., Boyarski, E., Bartak, R. (2019). Multi-agent pathfinding: Definitions, variants, and benchmarks. In: Symposium on Combinatorial Search (SoCS).
	
	\bibitem{sharon2015}
	Sharon, G., Stern, R., Felner, A., Sturtevant, N.R. (2015). Conflict-based search for optimal multi-agent pathfinding. \textit{Artificial Intelligence}, 219, 40–66.
	
	\bibitem{sharon2013}
	Sharon, G., Stern, R., Goldenberg, M., Felner, A. (2013). The increasing cost tree search for optimal multi-agent pathfinding. \textit{Artificial Intelligence}, 195, 470–495.
	
	
	\bibitem{bartk2017}
	Bartk, R., Zhou, N., Stern, R., Boyarski, E., Surynek, P. (2017). Modeling and solving the multi-agent pathfinding problem in Picat. In: \textit{IEEE International Conference on Tools with Artificial Intelligence (ICTAI)}, pp. 959–966.
	
	\bibitem{standley2010}
	Standley, T.S. (2010). Finding optimal solutions to cooperative pathfinding problems. In: \textit{AAAI Conference on Artificial Intelligence}, pp. 173–178.
	
	\bibitem{surynek2010}
	Surynek, P. (2010). An optimization variant of multi-robot path planning is intractable. In: \textit{AAAI Conference on Artificial Intelligence}.
	
	\bibitem{lau2022}
	Lau, T.T.-K., Sengupta, B. (2022). The Multi-Agent Pickup and Delivery Problem: MAPF, MARL and Its Warehouse Applications. \textit{arXiv preprint} arXiv:2203.07092. \url{https://doi.org/10.48550/arXiv.2203.07092}.
	
	\bibitem{silver2005}
	Silver, D. (2005). Cooperative Pathfinding. In: \textit{Proceedings of the AIIDE Conference}, pp. 117–122.
	
	\bibitem{ma2017}
	Ma, H., Li, J., Kumar, T.K.S., Koenig, S. (2017). Lifelong Multi-Agent Path Finding for Online Pickup and Delivery Tasks. In: \textit{Proceedings of the International Conference on Autonomous Agents and Multiagent Systems (AAMAS)}, pp. 837–845.
	
	\bibitem{xu2022}
	Xu, Q., Li, J., Koenig, S., Ma, H. (2022). Multi-Goal Multi-Agent Pickup and Delivery. \textit{2022 IEEE/RSJ International Conference on Intelligent Robots and Systems (IROS)}, Kyoto, Japan, pp. 9964–9971. \url{https://doi.org/10.1109/IROS47612.2022.9981785}.
	
	
	\bibitem{ma2017delay}
	Ma, H., Kumar, T.K.S., Koenig, S. (2017). Multi-Agent Path Finding with Delay Probabilities. In: \textit{Proceedings of the AAAI Conference}, pp. 3605–3612.
	
	\bibitem{walter2020}
	Wälter, J. (2020). Existing and Novel Approaches to the Vehicle Rescheduling Problem (VRSP) in the course of the Flatland Challenge by Swiss Federal Railways (SBB). University of Applied Sciences Rapperswil (HSR), Rapperswil, Switzerland. Supervisor: Prof. Dr. Farhad D. Mehta, External examiner: Dr. Xiaolu Rao. \url{https://api.semanticscholar.org/CorpusID:229937403}.
	
	
	\bibitem{li2021a}
	Li, J., Chen, Z., Harabor, D., Stuckey, P.J., Koenig, S. (2021). Anytime Multi-Agent Path Finding via Large Neighborhood Search: Extended Abstract. In: \textit{Proceedings of the AAMAS Conference}.
	
	\bibitem{atzmon2018}
	Atzmon, D., Stern, R., Felner, A., Wagner, G., Barták, R., Zhou, N.F. (2018). Robust Multi-Agent Path Finding. In: \textit{Proceedings of the International Symposium on Combinatorial Search}, AAAI Press, Washington, DC, USA, Volume 9, pp. 2–9.
	
	
	\bibitem{phillips2011}
	Phillips, M., Likhachev, M. (2011). SIPP: Safe Interval Path Planning for Dynamic Environments. In: \textit{Proceedings of the 2011 IEEE International Conference on Robotics and Automation}, Shanghai, China, 9–13 May, pp. 5628–5635.
	
	
	\bibitem{lin2021}
	Lin, B., Zhao, Y., Lin, R., Liu, C. (2021). Integrating Traffic Routing Optimization and Train Formation Plan Using Simulated Annealing Algorithm. \textit{Applied Mathematics Modeling}, 93, 811–830.
	
	\bibitem{svancara2022}
	Svancara, J., Barták, R. (2022). Tackling Train Routing via Multi-Agent Pathfinding and Constraint-Based Scheduling. In: \textit{ICAART}, pp. 306–313.
	
	\bibitem{he2023}
	He, Z., Li, Y., Li, H., Xu, N. (2023). Multi-Objective Optimization for Online Train Trajectory Planning with Moving Window Method. \textit{IAENG International Journal of Computer Science}, 50, 1074–1082.
	
	\bibitem{zhan2023}
	Zhan, Y., Ye, M., Zhang, R., He, S., Ni, S. (2023). Multi-Objective Optimization for Through Train Service Integrating Train Operation Plan and Type Selection. \textit{Transportation Letters}, 1–20.
	
	\bibitem{arsalani2023}
	Arsalani, P., Reisi-Nafchi, M., Dardashti, V., Moslehi, G. (2023). Two New Mixed-Integer Programming Models for the Integrated Train Formation and Shipment Path Optimization Problem. \textit{Networks}, 81, 359–377.
	
	\bibitem{atzmon2019}
	Atzmon, D., Diei, A., Rave, D. (2019). Multi-Train Path Finding. In: \textit{Proceedings of the International Symposium on Combinatorial Search}, AAAI Press, Washington, DC, USA, Volume 10, pp. 125–129.
	
	\bibitem{chen2022}
	Chen, Z., Li, J., Harabor, D., Stuckey, P.J., Koenig, S. (2022). Multi-Train Path Finding Revisited. In: \textit{Proceedings of the International Symposium on Combinatorial Search}, AAAI Press, Washington, DC, USA, Volume 15, pp. 38–46.
	
	\bibitem{miao2024}
	Miao, J., Li, P., Chen, C., Tian, J., Yang, L. (2024). MT-SIPP: An Efficient Collision-Free Multi-Chain Robot Path Planning Algorithm. \textit{Machines}, 12, 482. \url{https://doi.org/10.3390/machines12070482}.
	
	
	\bibitem{li2021flatland}
	Li, J., Chen, Z., Zheng, Y., Chan, S.-H., Harabor, D., Stuckey, P.J., Ma, H., Koenig, S. (2021). Scalable Rail Planning and Replanning: Winning the 2020 Flatland Challenge. \textit{Proceedings of the International Conference on Automated Planning and Scheduling}, 31(1), 477–485. \url{https://ojs.aaai.org/index.php/ICAPS/article/view/15994}. \url{https://doi.org/10.1609/icaps.v31i1.15994}.
	
	
	
	\bibitem{juliani2020}
	Juliani, A., Berges, V.-P., Teng, E., Cohen, A., Harper, J., Elion, C., Goy, C., Gao, Y., Henry, H., Mattar, M., Lange, D. (2020). Unity: A General Platform for Intelligent Agents. \textit{arXiv preprint arXiv:1809.02627}. \url{https://arxiv.org/pdf/1809.02627.pdf}.
	
	
	\bibitem{odin_inspector}
	Unity Asset Store. \textit{Odin Inspector and Serializer}. Available from: \url{https://assetstore.unity.com/packages/tools/utilities/odin-inspector-and-serializer-89041}.
	
	\bibitem{easy_save}
	Unity Asset Store. \textit{Easy Save - The Complete Save Game \& Data Serializer System}. Available from: \url{https://assetstore.unity.com/packages/tools/utilities/easy-save-the-complete-save-game-data-serializer-system-768}.
	
	\bibitem{shape_tool}
	Unity Asset Store. \textit{Shapes}. Available from: \url{https://assetstore.unity.com/packages/tools/particles-effects/shapes-173167}.
	
	\bibitem{feel_tool}
	Unity Asset Store. \textit{Feel}. Available from: \url{https://assetstore.unity.com/packages/tools/particles-effects/feel-183370}.
	
	\bibitem{dotween}
	Unity Asset Store. \textit{DOTween (HOTween v2)}. Available from: \url{https://assetstore.unity.com/packages/tools/animation/dotween-hotween-v2-27676}.
	
	\bibitem{path_creator}
	Unity Asset Store. \textit{Bézier Path Creator}. Available from: \url{https://assetstore.unity.com/packages/tools/utilities/b-zier-path-creator-136082}.
	
	
\end{thebibliography}